Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
snip reference
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@87 43ef1190-90fd-4dd7-a769-d0121f02b80e

Thus far, the benchmarking problem has been seen as a software testing
problem, but we could also ask if the existence of benchmark data can
be exposed to help federation query optimizers along with a
statistical digest.

@@

Fractional factorial design is covered in elementary text-books in
statistics but is most likely inadequate for this purpose, so I
intend to go further into the statistical literature to see if there
is methodology that is even better suited to the problem. Armed with
this, I hope to use amongst other things, the complexity analysis of
SPARQL (see e.g. \cite{Schmidt:2010:FSQ:1804669.1804675}) to find
suitable factors to see if my admittedly bold proposition that it is
possible to design a benchmark to cover all realistic cases.

>>>>

Thus far, the benchmarking problem has been seen as a software testing
problem, but as stated in the introduction this is not the only
objective, we may now see if benchmark data can be exposed to help
federation query optimizers along with a statistical digest.

@@

Fractional factorial design is covered in elementary text-books in
statistics but is most likely inadequate for this purpose, so I intend
to go further into the statistical literature to see if there is
methodology that is even better suited to the problem. Armed with
this, I hope to use amongst other things, the complexity analysis of
SPARQL to find suitable factors to see if my admittedly bold
proposition that it is possible to design a benchmark to cover all
realistic cases.
